### 2016-11-04 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd

Fig1D <- ggplot(temp,aes(y = DeltaRTL,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 2,label = 'D')

>>>>

temp <- dd3
dd3
props <- tapply(dd3$DeltaRTLF,dd3$TimeDiff,mean)
propn <- tapply(dd3$DeltaRTLF,dd3$TimeDiff,length)
temp <- data.frame(props,propn,TimeDiff = as.numeric(names(props))/12) %>%
  subset(propn > 10)

Fig1D <- ggplot(temp,aes(y = props,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 2,label = 'D')
